Quantum Interval-Valued Probability: Measurement and Probability

### 2017-08-29 prop_iop.tex
prop_iop.tex \subsection{Expectation Values for Classical IVPMs} Fix equation too long...
prop_iop.tex \subsection{Quantum {\normalsize{}$\mathscr{I}_{\mathrm{D}}$}-valued Probability Measures\label{subsec:Quantum-I_D-valued-Probability}} Updating...

\begin{definition}[Choquet integral~\cite{Vitali1925,Choquet1954,GilboaSchmeidler1994,Grabisch2016}]\label{def:Choquet}~
\begin{itemize}
\item Consider a classical IVPM~$\bar{\mu}$ such that $\mul:\events\rightarrow\left[0,1\right]$
and $\mur:\events\rightarrow\left[0,1\right]$ are the left-end and
the right-end of $\bar{\mu}$, respectively, i.e., $\bar{\mu}\left(E\right)=\left[\mul\left(E\right),\mur\left(E\right)\right]$.
\item We still decompose a random variable~$X$ into step functions, but
we separate the positive and negative terms and write like $\sum_{i=1}^{N^{-}}x_{i}^{-}\mathbf{1}_{E_{i}^{-}}+\sum_{i=1}^{N^{+}}x_{i}^{+}\mathbf{1}_{E_{i}^{+}}$,
i.e., 
\begin{equation}
x_{N^{-}}^{-}\le\ldots\le x_{1}^{-}\le0\le x_{1}^{+}\le\ldots\le x_{N^{+}}^{+}
\end{equation}
 and $\left\{ E_{i}^{-}\right\} _{i=1}^{N^{-}}$ and $\left\{ E_{i}^{+}\right\} _{i=1}^{N^{+}}$
are all disjoint.
\item Let $E_{i}^{s\prime}=\bigcup_{j\ge i}E_{j}^{s}$ and $\Delta\mu^{*}\left(E_{i}^{s\prime}\right)=\mu^{*}\left(E_{i}^{s\prime}\right)-\mu^{*}\left(E_{i+1}^{s\prime}\right)$,
where $s\in\left\{ +,-\right\} $ and $\mu^{*}\in\left\{ \mul,\mur\right\} $.
\end{itemize}
Then, the Choquet integral of $X$ with respect to $\bar{\mu}$ is
\begin{equation}
\int X\rmd\bar{\mu}=\left[\sum_{i=1}^{N^{+}}x_{i}^{+}\Delta\mul\left(E_{i}^{+\prime}\right)+\sum_{i=1}^{N^{-}}x_{i}^{-}\Delta\mur\left(E_{i}^{-\prime}\right),\sum_{i=1}^{N^{+}}x_{i}^{+}\Delta\mur\left(E_{i}^{+\prime}\right)+\sum_{i=1}^{N^{-}}x_{i}^{-}\Delta\mul\left(E_{i}^{-\prime}\right)\right]\,.\label{eq:interval-expectation}
\end{equation}
\end{definition}

@@

\begin{proof}Since $\left\{ \mathbf{O}_{j}\right\} $ is a sequence
of commuting observables, they can be diagonalized by a common orthonormal
basis\nb$\Omega=\left\{ \ket{k}\right\} _{k=0}^{d-1}$. By theorem~\ref{thm:sub-event-space},
there is a commuting sub-event space\nb$\widehat{\events}$ with
$\widehat{\events}\subseteq\events$ and a bijection\nb$\tau:\widehat{\events}\rightarrow2^{\Omega}$
such that there is a CIVPM\nb$\bar{\mu}:2^{\Omega}\rightarrow\mathscr{I}_{\mathrm{D}}$
such that $\bar{\mu}\left(P\right)=\bar{\mu}'\left(\tau\left(P\right)\right)$
for all $P\in\widehat{\events}$.

@@

>>>>

\begin{definition}[Choquet integral~\cite{Vitali1925,Choquet1954,GilboaSchmeidler1994,Grabisch2016}]\label{def:Choquet}~
\begin{itemize}
\item Consider a classical IVPM~$\bar{\mu}$ such that $\mul:\events\rightarrow\left[0,1\right]$
and $\mur:\events\rightarrow\left[0,1\right]$ are the left-end and
the right-end of $\bar{\mu}$, respectively, i.e., $\bar{\mu}\left(E\right)=\left[\mul\left(E\right),\mur\left(E\right)\right]$.
\item We still decompose a random variable~$X$ into step functions, but
we separate the positive and negative terms and write like $\sum_{i=1}^{N^{-}}x_{i}^{-}\mathbf{1}_{E_{i}^{-}}+\sum_{i=1}^{N^{+}}x_{i}^{+}\mathbf{1}_{E_{i}^{+}}$,
i.e., 
\begin{equation}
x_{N^{-}}^{-}\le\ldots\le x_{1}^{-}\le0\le x_{1}^{+}\le\ldots\le x_{N^{+}}^{+}
\end{equation}
 and $\left\{ E_{i}^{-}\right\} _{i=1}^{N^{-}}$ and $\left\{ E_{i}^{+}\right\} _{i=1}^{N^{+}}$
are all disjoint.
\item Let $E_{i}^{s\prime}=\bigcup_{j\ge i}E_{j}^{s}$ and $\Delta\mu^{*}\left(E_{i}^{s\prime}\right)=\mu^{*}\left(E_{i}^{s\prime}\right)-\mu^{*}\left(E_{i+1}^{s\prime}\right)$,
where $s\in\left\{ +,-\right\} $ and $\mu^{*}\in\left\{ \mul,\mur\right\} $.
\end{itemize}
Then, the Choquet integral of $X$ with respect to $\bar{\mu}$ is
\begin{equation}\eqalign{ 
\int X\rmd\bar{\mu} = & \left[\sum_{i=1}^{N^{+}}x_{i}^{+}\Delta\mul\left(E_{i}^{+\prime}\right)+\sum_{i=1}^{N^{-}}x_{i}^{-}\Delta\mur\left(E_{i}^{-\prime}\right),\right.\\  
& \left.\sum_{i=1}^{N^{+}}x_{i}^{+}\Delta\mur\left(E_{i}^{+\prime}\right)+\sum_{i=1}^{N^{-}}x_{i}^{-}\Delta\mul\left(E_{i}^{-\prime}\right)\right]\,.
}\label{eq:interval-expectation}\end{equation}
\end{definition}

@@

\begin{proof}[Proof 1]Since $\left\{ \mathbf{O}_{j}\right\} $ is
a sequence of commuting observables, they can be diagonalized by a
common orthonormal basis\nb$\Omega=\left\{ \ket{k}\right\} _{k=0}^{d-1}$.
By theorem~\ref{thm:sub-event-space}, there is a commuting sub-event
space\nb$\widehat{\events}$ with $\widehat{\events}\subseteq\events$
and a bijection\nb$\tau:\widehat{\events}\rightarrow2^{\Omega}$
such that there is a CIVPM\nb$\bar{\mu}:2^{\Omega}\rightarrow\mathscr{I}_{\mathrm{D}}$
such that $\bar{\mu}\left(P\right)=\bar{\mu}'\left(\tau\left(P\right)\right)$
for all $P\in\widehat{\events}$.

@@

\begin{proof}[Proof 2]Since $\left\{ \mathbf{O}_{j}\right\} $ is
a sequence of commuting observables, they can be diagonalized by a
common orthonormal basis\nb$\Omega=\left\{ \ket{k}\right\} _{k=0}^{d-1}$,
i.e., $\mathbf{O}_{j}=\sum_{k=0}^{d-1}\lambda_{j,k}\proj{k}$ and
$\prod_{j}\mathbf{O}_{j}=\sum_{k=0}^{d-1}\prod_{j}\lambda_{j,k}\proj{k}$.
By lemma~\ref{lemma:QIVPM2QCM}, $\mul$ and $\mur$ are the same
real-valued probability measures, and is simply denoted by $\mu:\events\rightarrow\left\{ 1,0\right\} $.
Since $\mu$ is a cryptodeterministic measure, there is only one $\proj{k}$
such that $\mu\left(\proj{k}\right)=1$.
\begin{eqnarray*}
 &  & \prod_{j}\expval{\mathbf{O}_{j}}_{\bar{\mu}}\stackrel{\textrm{Lemma }\ref{lemma:expectation-singleton}}{=}\prod_{j}\left\{ \expval{\mathbf{O}_{j}}_{\mu}\right\} \\
 & = & \prod_{j}\left\{ \lambda_{j,k}\right\} =\left\{ \prod_{j}\lambda_{j,k}\right\} \\
 & = & \expval{\prod_{j}\mathbf{O}_{j}}_{\mu}\stackrel{\textrm{Lemma }\ref{lemma:expectation-singleton}}{=}\expval{\prod_{j}\mathbf{O}_{j}}_{\bar{\mu}}\,.
\end{eqnarray*}
\end{proof}
